Commutative Character Sheaves

### 2015-11-12 followup.tex
Started work on Section 4, types.

A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
%so
%\begin{equation}\label{CS4}
%\begin{tikzcd}
%\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
%\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
%\end{tikzcd}
%\end{equation}
%commutes; see also [Dictionary, CS.4].
%
Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.

@@

\begin{proof} 
Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(m^*\cs{L}, m_2^*(\mu))$, where $m_2 : G\times G\times G\times G\to G\times G$ is defined by $m_2(x_1,y_1,x_2,y_2) = (m(x_1,x_2), m(y_1,y_2)$;
this can be seen by following the argument of [Dictionary].
Set $\cs{L}_2\ceq m^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
The linear character sheaf $(\cs{L}_2,\mu_2)$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ where $a_2 : H\times H\times G\times G\to G\times G$ is given by $a_2(h_1,g_1,h_2,g_2) = (a(h_1,g_1), a(h_2,g_2)$ and $p_2 : H\times H\times G\times G\to G\times G$ is given by $p_2(h_1,g_1,h_2,g_2)= ( g_1,g_2)$. 
The  isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ satisfies the appropriate version of \cite{ECS1}, so  $(\cs{L}_2,\mu_2,nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
Likewise $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
\end{tikzcd}
\]
Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
The appropriate version of \eqref{E3} also commutes, so $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism of equivariant linear character sheaves.
The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.
\end{proof}

@@

Now suppose $q : G \to G_0$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=2]{r}{a}
  \arrow[shift right=2,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G_0
\end{tikzcd}
\]
Let $\cs{L}_0$ be a linear character sheaf on $G_0$.
Consider the functor
\[
q^* : \CS(G_0) \to \CS(G)
\]
given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see [Dictionary, ].
%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify [Dictionary, CS.3], arguing as in [Dictionary].
This linear character sheaf $(\cs{L},\mu)\ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$ on $G$ comes equipped with the canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of canonical isomorphisms.
\[
\begin{tikzcd}
a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{rrr}{\nu} & & &  \arrow[equal]{d} p^*\cs{L} \\
a^* ( q^*\cs{L}_0) \arrow{r} 
& (q\circ a)^* \cs{L}_0 \arrow[equal]{r} 
& (q\circ p)^*\cs{L}_0 \arrow{r} 
& p^* q^*\cs{L}_0
\end{tikzcd}
\]
Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(G_0)$, 
then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies [Dictionary, CS.4], arguing as in [Dictionary], so $\alpha$ is a morphism in $\CS(G)$.
%\todo{I find myself having to make many references to [Dictionary] and promising that the results there adapt to the noncommutative group case. It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly. I'm just agonizing out loud, I guess.} 
These simple observations define the comparison functor
\[
q_H^* : \CS(G_0) \to CS_H(G)
\]
and show that the functor $q^* : \CS(G_0) \to \CS(G)$ factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(G_0) \arrow{dl}{q_H^*}\\
\arrow{u}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]
The definition of $q_H^* : \CS(G_0)\to \CS_H(G)$ will be revisited in the proof of the following result.

@@

We may now revisit the definition of the functor $q_H^*: \CS(Q)\to \CS_H(G)$.
By (a small part of) Lemma~\ref{lem:HH}, $\mu_0$ is a morphism of linear character sheaves on $G_0\times G_0$.
Thus, on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm [Definition, CS1, CS2, CS3], \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
Conditions [Definition, CS1, CS2, CS3] follow from an adaptation of [Dictionary, ...] while conditions \eqref{E1}, \eqref{E2} are a consequence of the work above. 
Condition \eqref{ECS1} is confirmed by brute force.
On maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
To verify that $L_1(\alpha_0)$ is a map in $\CS_H(G)$ we must confirm conditions [Definition, CS4] and \eqref{E3}.
Condition [Definition, CS4] follows from an adaptation of [Dictionary, ...] while condition \eqref{E3} is a consequence of the work above.

@@

Let $K$ be a local field with residue field $\Fq$.
Let $\underline{G}$ be a smooth group scheme over $K$.
Set $G_n = \Gr^R_n(\underline{G})$; this is a smooth group scheme over $\Fq$.
Set $G = \Gr_R(\underline{G})$; this is a group scheme over $\Fq$ equipped with $G = \varprojlim_{n\in \NN} G_n$.
Let $\QCS(G)$ be the category of commutative character sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.

\begin{proposition}\label{prop:QCS}
$\Hom(\underline{G}(\OK),\EEx) \iso \QCSiso{G}$.
\end{proposition}

>>>>

A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
%so
%\begin{equation}\label{CS4}
%\begin{tikzcd}
%\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
%\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
%\end{tikzcd}
%\end{equation}
%commutes; see also \cite{cunningham-roe:13a}, CS.4].
%
Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.

@@

\begin{proof} 
Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(m^*\cs{L}, m_2^*(\mu))$, where $m_2 : G\times G\times G\times G\to G\times G$ is defined by $m_2(x_1,y_1,x_2,y_2) = (m(x_1,x_2), m(y_1,y_2)$;
this can be seen by following the argument of \cite{cunningham-roe:13a}].
Set $\cs{L}_2\ceq m^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
The linear character sheaf $(\cs{L}_2,\mu_2)$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ where $a_2 : H\times H\times G\times G\to G\times G$ is given by $a_2(h_1,g_1,h_2,g_2) = (a(h_1,g_1), a(h_2,g_2)$ and $p_2 : H\times H\times G\times G\to G\times G$ is given by $p_2(h_1,g_1,h_2,g_2)= ( g_1,g_2)$. 
The  isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
Likewise $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
\end{tikzcd}
\]
Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
The appropriate version of \eqref{E3} also commutes, so $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism of equivariant linear character sheaves.
The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.
\end{proof}

@@

Now suppose $q : G \to G_0$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
\[
\begin{tikzcd}
H\times G
 \arrow[shift left=2]{r}{a}
  \arrow[shift right=2,swap]{r}{p}
&
G 
\arrow{r}{q}
& 
G_0
\end{tikzcd}
\]
Let $\cs{L}_0$ be a linear character sheaf on $G_0$.
Consider the functor
\[
q^* : \CS(G_0) \to \CS(G)
\]
given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see \cite{cunningham-roe:13a}*{}.
%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
This linear character sheaf $(\cs{L},\mu)\ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$ on $G$ comes equipped with the canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of canonical isomorphisms.
\[
\begin{tikzcd}
a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{rrr}{\nu} & & &  \arrow[equal]{d} p^*\cs{L} \\
a^* ( q^*\cs{L}_0) \arrow{r} 
& (q\circ a)^* \cs{L}_0 \arrow[equal]{r} 
& (q\circ p)^*\cs{L}_0 \arrow{r} 
& p^* q^*\cs{L}_0
\end{tikzcd}
\]
Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(G_0)$, 
then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, arguing as in \cite{cunningham-roe:13a} so $\alpha$ is a morphism in $\CS(G)$.
%\todo{I find myself having to make many references to \cite{cunningham-roe:13a}] and promising that the results there adapt to the noncommutative group case. It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly. I'm just agonizing out loud, I guess.} 
These simple observations define the comparison functor
\[
q_H^* : \CS(G_0) \to CS_H(G)
\]
and show that the functor $q^* : \CS(G_0) \to \CS(G)$ factors according to the following commuting diagram of functors
\[
\begin{tikzcd}
\CS(G) &\arrow{l}[swap]{q^*} 
\CS(G_0) \arrow{dl}{q_H^*}\\
\arrow{u}{\text{forget}} \CS_{H}(G). & 
\end{tikzcd}
\]
The definition of $q_H^* : \CS(G_0)\to \CS_H(G)$ will be revisited in the proof of the following result.

@@

We may now revisit the definition of the functor $q_H^*: \CS(Q)\to \CS_H(G)$.
By (a small part of) Lemma~\ref{lem:HH}, $\mu_0$ is a morphism of linear character sheaves on $G_0\times G_0$.
Thus, on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
Conditions \cite{cunningham-roe:13a}*{CS1, CS2, CS3} follow from an adaptation of \cite{cunningham-roe:13a}*{} while conditions \eqref{E1}, \eqref{E2} are a consequence of the work above. 
Condition \eqref{ECS1} is confirmed by brute force.
On maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
To verify that $L_1(\alpha_0)$ is a map in $\CS_H(G)$ we must confirm conditions \cite{cunningham-roe:13a}*{CS4} and \eqref{E3}.
Condition \cite{cunningham-roe:13a}*{CS4} follows from an adaptation of \cite{cunningham-roe:13a}*{} while condition \eqref{E3} is a consequence of the work above.

@@

Let $K$ be a local field with residue field $\Fq$.
Let $\underline{G}$ be a smooth group scheme over $K$.
Set $G_n = \Gr^R_n(\underline{G})$; this is a smooth group scheme over $\Fq$.
Set $G = \Gr_R(\underline{G})$; this is a group scheme over $\Fq$ equipped with $G = \varprojlim_{n\in \NN} G_n$.
Let $\QCS(G)$ be the category of commutative quasicharacter sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.

\begin{proposition}\label{prop:QCS}
$\Hom_\text{cts}(\underline{G}(\OK),\EEx) \iso \QCSiso{G}$.
\end{proposition}

\begin{proof}
\end{proof}
